---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# camtrapdp

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/camtraptor)](https://CRAN.R-project.org/package=camtrapdp)
[![CRAN checks](https://badges.cranchecks.info/worst/camtrapdp.svg)](https://cran.r-project.org/web/checks/check_results_camtrapdp.html)
[![R-CMD-check](https://github.com/inbo/camtrapdp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/inbo/camtrapdp/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/inbo/camtraptor/branch/main/graph/badge.svg)](https://app.codecov.io/gh/inbo/camtrapdp/)
[![repo status](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.11490269.svg)](https://doi.org/10.5281/zenodo.11490269)
<!-- badges: end -->

Camtrapdp is an R package to read and manipulate Camera Trap Data Packages (Camtrap DP). [Camtrap DP](https://camtrap-dp.tdwg.org) is a data exchange format for camera trap data. With camtrapdp you can read, filter and transform data (including to [Darwin Core](https://dwc.tdwg.org)) before further analysis in e.g. [camtraptor](https://inbo.github.io/camtraptor/) or [camtrapR](https://cran.r-project.org/package=camtrapR).

To get started, see:

- [Function reference](https://inbo.github.io/camtrapdp/reference/index.html): overview of all functions.

## Installation

Install the latest released version from CRAN:

```R
install.packages("camtrapdp")
```

Or the development version from [GitHub](https://github.com/inbo/camtrapdp):

```r
# install.packages("devtools")
devtools::install_github("inbo/camtrapdp")
```

## Usage

With camtrapdp you can **read** a Camtrap DP dataset into your R environment:

```{r}
library(camtrapdp)

file <- "https://raw.githubusercontent.com/tdwg/camtrap-dp/1.0/example/datapackage.json"
x <- read_camtrapdp(file)
x
```

`read_camtrapdp()` will automatically **convert** an older version of Camtrap DP to the latest version. It will also make the data easier to use, by assigning taxonomic information (found in the metadata) to the observations and `eventID`s (found in the observations) to the media.

To **access** the data, use one of the [accessor functions](https://inbo.github.io/camtrapdp/reference/index.html#accessor-and-assignment-functions) like `locations()`:

```{r}
locations(x)
```

You can also **filter** data with one of the [filter functions](https://inbo.github.io/camtrapdp/reference/index.html#filter-functions), which automatically filter the related data. For example, here we filter observations on scientific name(s) and return the associated events in that subset:

```{r}
x %>%
  filter_observations(
    scientificName %in% c("Martes foina", "Mustela putorius")
  ) %>%
  events()
```

For more functionality, see the [function reference](https://inbo.github.io/camtrapdp/reference/index.html).

## Meta

- We welcome [contributions](https://inbo.github.io/camtrapdp/CONTRIBUTING.html) including bug reports.
- License: MIT
- Get [citation information](https://inbo.github.io/camtrapdp/authors.html#citation) for camtrapdp in R doing `citation("camtrapdp")`.
- Please note that this project is released with a [Contributor Code of Conduct](https://inbo.github.io/camtrapdp/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
